### 2025-07-11 factor-analysis.qmd
20250710 - lavaanPlot2()

A path diagram of the EFA model in @fig-efaPathDiagram-3factor was created using the `lavaanPlot()` function of the `lavaanPlot` package [@R-lavaanPlot].

@@

lavaanPlot::lavaanPlot(
  efa_fit$nf3,
  coefs = TRUE,
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot(
  efa3factor_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot(
  efa3factorModified_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

@@

lavaanPlot::lavaanPlot(
  cfa1factor_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot(
  cfa2factor_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot(
  cfa3factor_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot(
  cfa3factorModified_fit,
  coefs = TRUE,
  stand = TRUE)
```

>>>>

A path diagram of the EFA model in @fig-efaPathDiagram-3factor was created using the `lavaanPlot2()` function of the `lavaanPlot` package [@R-lavaanPlot].

@@

lavaanPlot::lavaanPlot2(
  efa_fit$nf3,
  include = "covs"
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot2(
  efa3factor_fit,
  include = "covs"
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot2(
  efa3factorModified_fit,
  include = "covs"
  stand = TRUE)
```

@@

```{r}
dataForFA[which.max(efa3factorModified_factorScores[,"F3"]), c("player_display_name", "season", factor3vars)]
```

@@

lavaanPlot::lavaanPlot2(
  cfa1factor_fit,
  include = "covs"
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot2(
  cfa2factor_fit,
  include = "covs"
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot2(
  cfa3factor_fit,
  include = "covs"
  stand = TRUE)
```

@@

lavaanPlot::lavaanPlot2(
  cfa3factorModified_fit,
  include = "covs"
  stand = TRUE)
```
